Carbonate chemistry at Ny-Ålesund

### 2021-04-09 awipev-CO2.Rmd
read new file with depth_complete

```{r read observatory data, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::filter(datetime <= as.POSIXct("2021-01-10")) %>% #cutoff date
  dplyr::select(-pco2_inst) %>% # this is the serial number of pCO2 sensor, not needed
  dplyr::rename(
    pco2_fb = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  arrange(datetime)
d_all <- as_tibble(d_hour) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & pressure_insitu_ctd <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & pressure_insitu_ctd <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & pressure_insitu_ctd <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 10, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                year = lubridate::year(d_hour$datetime), # year as a number
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
  )
rm(d_hour)
```

@@

#nuts <- tibble(Pair = "pCO2-AT", "CT-AT",
#)
nuts_table <- bind_rows(diff_po4_0a, diff_Si_0a, diff_po4_0b, diff_Si_0b, diff_max_0a, diff_max_0b) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "pCO2 and ALK", "ALK and DIC", "ALK and DIC", "ALK and DIC", "ALK and DIC"),
                nutrients = c("No PO4-max PO4", "No Si-max Si", "No PO4-max PO4", 
                              "No Si-max Si", "No nuts-max nuts", "No nuts-max nuts")) %>% 
  dplyr::select(flag, nutrients, pH, pCO2, DIC, OmegaAragonite)
rm(ts_po4_bp, ts_Si_bp)
```
`r knitr::kable(nuts_table, digits = c(1, 1, 4, 2, 4, 3), caption = "Impact of PO4 and Si.", format = "simple")`

>>>>

```{r read observatory data, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::filter(datetime <= as.POSIXct("2021-01-10")) %>% #cutoff date
  dplyr::select(-pco2_inst) %>% # this is the serial number of pCO2 sensor, not needed
  dplyr::rename(
    pco2_fb = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  arrange(datetime)
# read a file provided by Philipp for reconstructing missing pressure data
svl_remos_depth <- tibble(
  readRDS(file = paste0(
    path,
    "fb_data/svl_remos_depth.rds"
  )))
d_hour <- dplyr::left_join(d_hour, svl_remos_depth, by = 'datetime') %>% 
  dplyr::select(-adcp_fill, -ctd_fill)
d_all <- as_tibble(d_hour) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & pressure_insitu_ctd <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & pressure_insitu_ctd <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & pressure_insitu_ctd <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 10, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                year = lubridate::year(d_hour$datetime), # year as a number
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
  )
rm(d_hour)
```

@@

#nuts <- tibble(Pair = "pCO2-AT", "CT-AT",
#)
nuts_table <- bind_rows(diff_po4_0a, diff_Si_0a, diff_po4_0b, diff_Si_0b, diff_max_0a, diff_max_0b) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "pCO2 and ALK", "ALK and DIC", "ALK and DIC", "pCO2 and AT", "ALK and DIC"),
                nutrients = c("No PO4-max PO4", "No Si-max Si", "No PO4-max PO4", 
                              "No Si-max Si", "No nuts-max nuts", "No nuts-max nuts")) %>% 
  dplyr::select(flag, nutrients, pH, pCO2, DIC, OmegaAragonite)
rm(ts_po4_bp, ts_Si_bp)
```
`r knitr::kable(nuts_table, digits = c(1, 1, 4, 2, 7, 3), caption = "Impact of PO4 and Si.", format = "simple")`
